---
output: html_document
editor_options: 
  chunk_output_type: console
---
Scripts associated with data analysis for the Masig Island sugar feeding study.

Load these packages for model testing only (not compatabile with the other chunk of packages)

```{r}
library(tidyverse)
library(performance)
library(lme4)
library(qqplotr)
```

Loading packages
```{r}
library(qtl)
library(ggplot2)
library(pscl)
library(boot)
library(psych) 
library(stats) 
library(MASS)
library(car)
library(lmtest)
library(lme4)
library(tidyverse)
library(tibble)
library(aods3)
library(emmeans)
library(dplyr)
library(MuMIn)
library(blmeco)
library(cowplot)
library(ResourceSelection)
library(ggrepel)
library(arm)
library(glmmTMB)
library(knitr)
library(vegan)
library(jtools)
library(sjPlot)
library(stargazer)
library(ggpubr)
library(performance)
library(see)
library(broom)
library(qqplotr)
```

```{r}
#Import the data
#Using Aedes Albopictus negative controls (mean + SD*2) as the fructose cut off

albo_TSI_data_2SD <- read.csv(file = "TSI_data_albo_cutoff_2SD.csv")

#convert the sugar integer to a factor

nd_TSI_data_2SD_plots <- albo_TSI_data_2SD %>% mutate(sugar= as.factor(sugar))

#confirm that this is now a factor. 
str(nd_TSI_data_2SD_plots)

#create this positions to get the right order. 
positions_time <- c("Morning", "Afternoon")

```

Summary statistics

```{r}

# proportion sugar fed at each habitat

habitat_sugar_per_station <- nd_TSI_data_2SD_plots %>% 
                      group_by(habitat, sex, sugar) %>%
                      summarise(samp = n()) %>%
                      mutate(percent=prop.table(samp)*100)

#proportion sugar fed at each station

sugar_per_station <- nd_TSI_data_2SD_plots %>% 
                      group_by(station, sugar) %>%
                      summarise(samp = n()) %>%
                      mutate(percent=prop.table(samp)*100)

#does not appear to be significantly different

#add the sample size to each plot

nd_TSI_data_plots_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(habitat) %>% 
                         summarise(samp = n())
  
nd_TSI_data_plots_sum

#get the sum of sugar by visual examination

nd_TSI_data_plots_visual_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(sugar,sex, contents) %>% 
                         summarise(samp = n())

#get the sum of sugar by habitat, station and sex

nd_TSI_data_plots_visual_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(sugar, sex, time) %>% 
                         summarise(samp = n())

#get the sum of mosquitoes captured by day ,station and sex

day_TSI_data_plots_visual_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(day, station, habitat, sex) %>% 
                         summarise(samp = n()) %>% as_tibble()

#summary of day and station level:

time_day_TSI_day_station <- nd_TSI_data_2SD_plots %>% 
                         group_by(day, time,station, sex) %>% 
                         summarise(samp = n()) 


str(day_TSI_data_plots_visual_sum)

#group by flowers binary

TSI_day_flowers_sex_sugar <- nd_TSI_data_2SD_plots %>% 
                         group_by(flowers_binary, sex,sugar) %>% 
                         summarise(samp = n()) 

TSI_time <- nd_TSI_data_2SD_plots %>% 
                         group_by(time, sex,sugar) %>% 
                         summarise(samp = n()) 

TSI_habitat <- nd_TSI_data_2SD_plots %>% 
                         group_by(habitat, sex,sugar) %>% 
                         summarise(samp = n()) 

#average fructose concentration by habitat, time and flowers

describeBy(nd_TSI_data_2SD_plots, nd_TSI_data_2SD_plots$habitat+nd_TSI_data_2SD_plots$fructose_concentration)



#but you want to include only the positive mosquitoes, so you would need to filter this by positive only (and include bins for flowers)
aggregate(formula = fructose_concentration ~ habitat + sex,
          data = nd_TSI_data_2SD_plots, FUN = sum)

```

GLMM for the following model 
```{r}
albo_TSI_data_2SD_glmer <- glmer(sugar ~ time*sex+habitat+flowers_binary+(1|day) + (1|station), family = binomial, data = albo_TSI_data_2SD)
Anova(albo_TSI_data_2SD_glmer)
summary(albo_TSI_data_2SD_glmer)
summ(albo_TSI_data_2SD_glmer)

hoslem.test(albo_TSI_data_2SD$sugar, fitted(albo_TSI_data_2SD_glmer))

#when using the 2 SD data, the H-L fit is not significant.

tab_model(albo_TSI_data_2SD_glmer, show.se = T) 

#seeing whether habitat and flowers binary correlate

coef(albo_TSI_data_2SD_glmer)

```

GLMM for a model with EFNs (overall model)

```{r}
albo_TSI_EFN_model_glmer <- glmer(sugar ~ time+sex+habitat+EFN+(1|day) + (1|station), family = binomial, data = albo_TSI_data_2SD)
Anova(albo_TSI_EFN_model_glmer)

#when I run all the variables in the model - the EFN does not come out. This warning 'fixed-effect model matrix is rank deficient so dropping 1 column / coefficient'. The EFN does not occur in the woodland habitats, so not able to have a valid comparison. 

#insignificant - p = 0.09
```

Plotting the male 2 SD data
```{r}

#filter this by the male data, instead of importing another sheet.

albo_male_2SD <- albo_TSI_data_2SD %>% filter(sex == "Male")

#old way before filtering
#albo_male_2SD <- read.csv(file = "TSI_data_albo_male_2SD.csv")

albo_male_2SD_plots <- albo_male_2SD %>% mutate(sugar= as.factor(sugar))

#confirm that this is now a factor. 
str(albo_male_2SD_plots)

male_only_2SD <- glmer(sugar ~ time+ habitat+ flowers_binary+(1|day) + (1|station), family = binomial, data = albo_male_2SD)
summary(male_only_2SD)
Anova(male_only_2SD)

#kable(male_Anova, digits = 3)

summ(male_only_2SD)

tab_model(male_only_2SD, show.stat = T, show.se = T, show.intercept = T, show.fstat = T, show.est = T)

tab_model(male_only_2SD, show.est = T, show.se = T)

#only time is significant for the males.
#interesting. When I plot this by males only, the significance of habitat is not there. 

hoslem.test(albo_male_2SD$sugar, fitted(male_only_2SD))
#highly insignicant

#time for male albopictus - more male albopictus is sugar fed in the morning. 
albo_male_2SD_plots %>% ggplot(mapping = aes(x=time, fill=sugar)) + geom_bar(position="fill") + scale_x_discrete(limits=positions_time) + labs(x= "Time", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#habitat for male albopictus
albo_male_2SD_plots %>% ggplot(mapping = aes(x=habitat, fill=sugar)) + geom_bar(position="fill") + labs(x= "Habitat", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#%sugar fed AM and PM
                      time_sugar <- albo_male_2SD_plots %>% 
                      group_by(time, sugar) %>%
                      summarise(samp = n()) %>%
                      mutate(percent=prop.table(samp)*100)

#habitat_sugar                      
                      habitat_sugar_male <- albo_male_2SD_plots %>% 
                      group_by(habitat, sugar) %>%
                      summarise(samp = n()) %>%
                      mutate(percent=prop.table(samp)*100)                      
                      
```

GLMM for a model with males only EFNs (male-only model)

```{r}
EFN_male_only_2SD <- glmer(sugar ~ EFN+(1|day) + (1|station), family = binomial, data = albo_male_2SD)
summary(EFN_male_only_2SD)
Anova(EFN_male_only_2SD)

#when I run all the variables in the model - the EFN does not come out. This warning 'fixed-effect model matrix is rank deficient so dropping 1 column / coefficient'. The EFN does not occur in the woodland habitats, so not able to have a valid comparison. 

#highly insignificant.
```

Plotting the female 2 SD data
```{r}

albo_female_2SD <- albo_TSI_data_2SD %>% filter(sex == "Female")

#Import the data

#albo_female_2SD <- read.csv(file = "TSI_data_albo_female_2SD.csv")

#convert this to a factor

#convert the sugar integer to a factor

albo_female_2SD_plots <- albo_female_2SD %>% mutate(sugar= as.factor(sugar))

#confirm that this is now a factor. 
str(albo_female_2SD_plots)

#running the model

female_only_2SD <- glmer(sugar ~ time+habitat+flowers_binary+(1|day) + (1|station), family = binomial, data = albo_female_2SD)
summary(female_only_2SD)
summ(female_only_2SD)
Anova(female_only_2SD)
#depending on which terms are included in the model. Flowers_binary is insignificant for this model.

hoslem.test(albo_female_2SD$sugar, fitted(female_only_2SD))
#highly insignicant

tab_model(female_only_2SD, show.se = T, show.intercept = T, show.fstat = T)


#plot sugar feeding by sex and time

#time for females albopictus - more female albopictus is sugar fed in the morning. 
albo_female_2SD_plots %>% ggplot(mapping = aes(x=time, fill=sugar)) + geom_bar(position="fill") + scale_x_discrete(limits=positions_time) + labs(x= "Time", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#order them by morning and afternoon

positions_time <- c("Morning", "Afternoon")

#habitat for females albopictus - more female albopictus is sugar fed in the urban environment. 
albo_female_2SD_plots %>% ggplot(mapping = aes(x=habitat, fill=sugar)) + geom_bar(position="fill") + labs(x= "Habitat", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#plot of proportion sugar fed by flowers_binary_bins

#%sugar fed AM and PM
                      time_sugar_female <- albo_female_2SD_plots %>% 
                      group_by(time, sugar) %>%
                      summarise(samp = n()) %>%
                      mutate(percent=prop.table(samp)*100)

#habitat_sugar                      
                      habitat_sugar_female <- albo_female_2SD_plots %>% 
                      group_by(habitat, sugar) %>%
                      summarise(samp = n()) %>%
                      mutate(percent=prop.table(samp)*100)
```

GLMM for a model with females only EFNs (female-only model)

```{r}
EFN_female_only_2SD <- glmer(sugar ~ time+habitat+ EFN+(1|day) + (1|station), family = binomial, data = albo_female_2SD)
summary(EFN_female_only_2SD)
summ(EFN_female_only_2SD)
Anova(EFN_female_only_2SD)

#when I run all the variables in the model - the EFN does not come out. This warning 'fixed-effect model matrix is rank deficient so dropping 1 column / coefficient'. The EFN does not occur in the woodland habitats, so not able to have a valid comparison. 

#highly insignificant.
```

Importing the TSI_data_positive
```{r}

TSI_data_positive <- albo_TSI_data_2SD %>% filter(sugar =="1")

```


Fitting a linear model to determine the impact of measured variables on log fructose content for the positive mosquitoes 

```{r}

logmodel_fructose_content <- lmer(log(fructose_content) ~ sex + habitat+ time+ flowers_binary + (1|day) + (1|station), data = TSI_data_positive)
summary(logmodel_fructose_content)
summ(logmodel_fructose_content)
Anova(logmodel_fructose_content)

plot(logmodel_fructose_content)

#look at the model assumptions

check_model(logmodel_fructose_content)
#only works with some packages loaded. The log fructose content is defo the way to go. The not logged one violates a number of these assumptions.

model_performance(logmodel_fructose_content)
#lower AIC weight than model w/o log.

tab_model(logmodel_fructose_content, show.se = T)

#sex [Male] has significantly lower fructose content than female.

overall_fructose_content_habitat <- describeBy(TSI_data_positive, TSI_data_positive$time)

```

Fitting EFNs with the log model
```{r}
EFN_logmodel_fructose_content <- lmer(log(fructose_content) ~ EFN + (1|day) + (1|station), data = TSI_data_positive)
summary(EFN_logmodel_fructose_content)
summ(EFN_logmodel_fructose_content)
Anova(EFN_logmodel_fructose_content)


```

Plot of fructose content by sex
```{r}
#overall figure

#to try and get the order for morning and then afternoon
TSI_data_positive$time2 <- factor(TSI_data_positive$time, levels=c("Morning", "Afternoon"))

#Fig b
TSI_data_positive %>% ggplot(mapping = aes(x=sex, y=log(fructose_content), fill = time2)) + scale_fill_discrete(limits=positions_time) + geom_boxplot() + labs(x="", y=expression("log fructose content ("~mu*"g)"), fill ="Time") + theme_cowplot()
```

Model for males and females (to avoid the simpson's paradox)

Males only positive
```{r}
#import male only data

TSI_male_positive <- albo_TSI_data_2SD %>% filter(sex =="Male", sugar == "1")

#TSI_male_positive <- read.csv("Male_2SD_positive.csv")
str(TSI_male_positive)

TSI_male_positive_n <- TSI_male_positive %>%
                        group_by(habitat, time) %>%
                        summarise(samp = n())

#summarise average fructose content by different categories

male_fructose_content_habitat <- describeBy(TSI_male_positive, TSI_male_positive$habitat)

male_fructose_content_time <- describeBy(TSI_male_positive, TSI_male_positive$time)
  
male_fructose_content_time_flower <- describeBy(TSI_male_positive, TSI_male_positive$flowers_binary) 

male_fructose_content_physiological <- describeBy(TSI_male_positive, TSI_male_positive$contents)


male_fructose_content <- lmer(log(fructose_content) ~ time+habitat+flowers_binary + (1|day) + (1|station), data = TSI_male_positive)


#log transforming the fructose makes a big difference. This suggests that the fructose concentration varies by time of day for the males. 
plot(male_fructose_content)


model_performance(male_fructose_content)

Anova(male_fructose_content)
summ(male_fructose_content)

male_time_habitat <- emmeans(male_fructose_content, list(pairwise ~ time), adjust = "tukey")
male_time_habitat
#significantly higher fructose content in the morning than the afternoon for males. 

tab_model(male_fructose_content, show.se = T)


```

ggplot of fructose concentration for the males
```{r}

TSI_male_positive %>% ggplot(mapping = aes(x=time, y=log(fructose_content))) +geom_point() + geom_boxplot() + scale_x_discrete(limits=positions_time) + labs(x= "Time", y = "log fructose content (ug/uL)") + theme_cowplot()
```

Females only positive
```{r}
#importing the data
TSI_female_positive <- albo_TSI_data_2SD %>% filter(sex =="Female", sugar == "1")

#TSI_female_positive <- read.csv("Female_2SD_positive.csv")
str(TSI_female_positive)

female_fructose_content_habitat <- describeBy(TSI_female_positive, TSI_female_positive$habitat)

female_fructose_content_time <- describeBy(TSI_female_positive, TSI_female_positive$time)
  
female_fructose_content_time_flower <- describeBy(TSI_female_positive, TSI_female_positive$flowers_binary)  

female_fructose_content_physiological <- describeBy(TSI_female_positive, TSI_female_positive$contents)

#log fructose content and add as a new column.I should try this.

female_fructose <- lmer(log(fructose_content) ~ time+habitat+flowers_binary + (1|day) + (1|station), data = TSI_female_positive)
Anova(female_fructose)
summary(female_fructose)

summ(female_fructose)

plot(female_fructose)

#not significant higher fructose concentration in the morning than the afternoon for females. 

model_performance(female_fructose)

tab_model(female_fructose, show.se = T)

```

Females only fitting EFN by log fructose content

```{r}
EFN_female_fructose <- lmer(log(fructose_content) ~ EFN + (1|day) + (1|station), data = TSI_female_positive)
Anova(EFN_female_fructose)
```


Figure 2: visual examination to detect sugar in mossies
```{r}

#Our visual examination was able to detect the presence of sugar for nearly all mossies that were clear. Unfed it could not dectet very well. 

#proportion

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=contents, fill=sugar)) + geom_bar(position="fill")+ labs(x= "Visual examination", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))

```

Figure of the cut offs for mean + SDs

```{r}

albo_data_cutoff <- read.csv("albo_data_cutoffs.csv")

#female only 
female_albo_data_cutoff <- albo_data_cutoff %>% filter(sex == "Female")

#male only 
male_albo_data_cutoff <- albo_data_cutoff %>% filter(sex == "Male")

#also import the sex-specific cut-off fructose concentration values, to plot these in R. 
#save it as a file with 1. mean absorbance, 2. fructose concentration, 3. sex

albo_male_female_negatives <- read.csv("Albo_negative_controls_female_male_all.csv")

#female only
female_negatives <- albo_male_female_negatives %>% filter(sex == "Female")

#male only

male_negatives <- albo_male_female_negatives %>% filter(sex == "Male")

```

Fructose content with the field data + the lab cut-offs

```{r}

ggplot() + geom_point(data= female_albo_data_cutoff, aes(x=sex, y=log(fructose_concentration)), position = "jitter", colour = "grey") + geom_point(data = albo_male_female_negatives, aes(x=sex, y=log(fructose_concentration)), position = "jitter", colour = "red")

#try the female with the cut offs
albo_female_with_negatives <- albo_data_cutoff %>% filter(sex == "Female") %>% ggplot(mapping = aes(x=sex, y=log(fructose_content)))+ geom_boxplot()+ geom_point(position = "jitter") + geom_point(data= female_negatives, position = "jitter", color = "orange")+ geom_hline(yintercept=log(0.754588483), lty="solid", col = "red")+ geom_hline(yintercept = log(1.854383075), lty="dotted", col = "red")+ geom_hline(yintercept = log(2.954177668), lty="longdash", col = "red") + geom_hline(yintercept = log(4.05397226), lty="twodash", col = "red") + labs(x= "", y = "Log fructose content ("~mu*"g)", fill ="Time") + theme_cowplot()

#+ scale_y_continuous(limits = c(-6.5, 0))
  
  
#try the male with the cutoffs

albo_male_with_negatives <- albo_data_cutoff %>% filter(sex == "Male") %>% ggplot(mapping = aes(x=sex, y=log(fructose_content)))+ geom_boxplot()+ geom_point(position = "jitter") + geom_point(data = male_negatives, position = "jitter", color = "orange") + geom_hline(yintercept=log(0.60779043), lty="solid", col = "red")+ geom_hline(yintercept = log(1.464166454), lty="dotted", col = "red")+ geom_hline(yintercept = log(2.320542478), lty="longdash", col = "red") + geom_hline(yintercept = log(3.176918502), lty="twodash", col = "red") + labs(x= "", y = "Log fructose content ("~mu*"g)", fill ="Time") + theme_cowplot() 

ggarrange(albo_female_with_negatives,albo_male_with_negatives)

#change this to content if you want to include in ms.

```

This one is with the field data only showing fructose concentration
```{r}
#maybe just do by females and then by males and then facet_wrap the two together.

#with the female cut offs only.

female_albo_cutoff <- albo_data_cutoff %>% filter(sex == "Female") %>% ggplot(mapping = aes(x=sex, y=log(fructose_concentration)))+ geom_boxplot()+ geom_point(position = "jitter") + geom_hline(yintercept=log(0.001775502), lty="solid", col = "red")+ geom_hline(yintercept = log(0.004800524), lty="dotted", col = "red")+ geom_hline(yintercept = log(0.006951006), lty="longdash", col = "red") + geom_hline(yintercept = log(0.009538758), lty="twodash", col = "red") + labs(x= "", y = "Log fructose concentration (ug/uL)", fill ="Time") + theme_cowplot()

#with the male cutoffs only:

male_albo_cutoff <- albo_data_cutoff %>% filter(sex == "Male") %>% ggplot(mapping = aes(x=sex, y=log(fructose_concentration)))+ geom_boxplot()+ geom_point(position = "jitter") + geom_hline(yintercept=log(0.001430095), lty="solid", col = "red")+ geom_hline(yintercept = log(0.003445098), lty="dotted", col = "red")+ geom_hline(yintercept = log(0.0054601), lty="longdash", col = "red") + geom_hline(yintercept = log(0.007475102), lty="twodash", col = "red") + labs(x= "", y = "Log fructose concentration (ug/uL)", fill ="Time") + theme_cowplot()

ggarrange(female_albo_cutoff,male_albo_cutoff)

```

Looking at n and % for each category
```{r}
#use the summarise function - this worked for mean.

albo_mean_cutoff <- albo_data_cutoff %>% 
  group_by(sex, mean) %>% 
  summarise(samp = n()) %>%
  mutate(percent =prop.table(samp)*100) 

albo_mean_1SD_cutoff <- albo_data_cutoff %>% 
  group_by(sex, mean_1SD) %>% 
  summarise(samp = n()) %>%
  mutate(percent=prop.table(samp)*100)


albo_mean_2SD_cutoff <- albo_data_cutoff %>% 
  group_by(sex, mean_2SD) %>% 
  summarise(samp = n()) %>%
  mutate(percent=prop.table(samp)*100)

albo_mean_3SD_cutoff <- albo_data_cutoff %>% 
  group_by(sex, mean_3SD) %>% 
  summarise(samp = n()) %>%
  mutate(percent=prop.table(samp)*100)

#didn't quite work for the Female N - Female P.
    
#add the sample size to each plot

nd_TSI_data_plots_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(habitat) %>% 
                         summarise(samp = n())
  
nd_TSI_data_plots_sum

```

```{r}

versionInfo(RStudio.Version())

RStudio.Version()

citation()
```

