---
output: html_document
editor_options: 
  chunk_output_type: console
---
Scripts concerned with data analysis for the Masig Island sugar feeding study.


Loading packages
```{r}
library(qtl)
library(ggplot2)
library(pscl)
library(boot)
library(psych) 
library(stats) 
library(MASS)
library(car)
library(lmtest)
library(lme4)
library(tidyverse)
library(tibble)
library(aods3)
library(emmeans)
library(dplyr)
library(MuMIn)
library(DHARMa)
library(blmeco)
library(cowplot)
library(ResourceSelection)
library(ggrepel)
library(arm)
library(glmmTMB)

```

```{r}
#Import the data
#Using Aedes Albopictus negative controls (mean + SD*2) as the fructose cut off

albo_TSI_data_2SD <- read.csv(file = "TSI_data_albo_cutoff_2SD.csv")

```

Summary statistics

```{r}

#convert the sugar integer to a factor

nd_TSI_data_2SD_plots <- albo_TSI_data_2SD %>% mutate(sugar= as.factor(sugar))

#confirm that this is now a factor. 
str(nd_TSI_data_2SD_plots)

#add the sample size to each plot

nd_TSI_data_plots_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(sugar,sex, habitat,time) %>% 
                         summarise(samp = n())
  
nd_TSI_data_plots_sum

#get the sum of sugar by visual examination

nd_TSI_data_plots_visual_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(sugar,sex, contents) %>% 
                         summarise(samp = n())

#get the sum of sugar by habitat, station and sex

nd_TSI_data_plots_visual_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(sugar, sex, time) %>% 
                         summarise(samp = n())

#create this positions to get the right order. 
positions_time <- c("Morning", "Afternoon")

```

Figure 1: Count of sugar fed status by time of day for both male and female Aedes albopictus
```{r}
#1. Figure: Count of sugar fed status by time of day for both male and female Aedes albopictus. would be good to include the n in this. 
#why are males more sugar fed in the morning compared to females?
#think about a facet_grid for comparing count with sex, facetted by time of day. #this one shows that more females than males were captured in both the morning and afternoon.

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=sex, fill=sugar)) + geom_bar(position="dodge") + facet_grid(~fct_rev(time)) + labs(x= "Sex", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()

#this graph here shows proportion of sex sugar fed.
nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=sex, fill=sugar)) + geom_bar(position="fill") + facet_grid(~fct_rev(time)) + labs(x= "Sex", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#sex

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=sex, fill=sugar)) + geom_bar(position="fill") + labs(x= "Sex", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#time
nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=time, fill=sugar)) + geom_bar(position="fill") + scale_x_discrete(limits=positions_time) + labs(x= "Time", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#habitat
nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=habitat, fill=sugar)) + geom_bar(position="fill") + labs(x= "", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()
```

Figure 2: visual examination to detect sugar in mossies
```{r}

#Our visual examination was able to detect the presence of sugar for nearly all mossies that were clear. Unfed it could not dectet very well. 

#count

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=contents, fill=sugar)) + geom_bar(position="dodge")+ labs(x= "Visual examination", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=contents, fill=sugar)) + geom_bar(position="dodge")+ labs(x= "Visual examination", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))

#proportion.

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=contents, fill=sugar)) + geom_bar(position="fill")+ labs(x= "Visual examination", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) + theme_cowplot()

```

```{r}
#Figure 3: Habitat, sex and sugar - not used 
#count

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=sex, fill=sugar)) + geom_bar(position="dodge") + facet_grid(~fct_rev(habitat)) + labs(x= "Sex", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()

#add mean + standard error.

#proportion

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=sex, fill=sugar)) + geom_bar(position="fill") + facet_grid(~fct_rev(habitat)) + labs(x= "Sex", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot() 


#try adding the geom_text information with the nd_TSI_plots_sum text 
#ggplot(nd_TSI_data_plots, mapping = aes(x=sex, fill=sugar)) + geom_bar(position="dodge") + facet_grid(~fct_rev(habitat)) + labs(x= "Sex", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ geom_text_repel(data= nd_TSI_data_plots_sum, mapping = aes(label=samp, y= 50)) + theme_cowplot()


#Fig x: time of day and sugar

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=time, fill=sugar)) + geom_bar(position="fill") + labs(x= "time", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()

#Fig x: habitat with time of day
nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=habitat, fill=sugar)) + geom_bar(position="fill") + facet_grid(~fct_rev(time)) + labs(x= "habitat", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()

#habitat only 

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=habitat, fill=sugar)) + geom_bar(position="dodge") + labs(x= "habitat", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()

#Fig x: sex
nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=sex, fill=sugar)) + geom_bar(position="fill") + labs(x= "Sex", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()
```

```{r}
#did not use
#More females than males captured in the urban environment. #more male albopictus captured in the bush than in the urban habitat.
nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x =sex, fill=habitat)) + geom_bar(position = "dodge")

#time of day - more female captured in the afternoon 
nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x =sex, fill=time)) + geom_bar(position = "dodge")

#maybe look at fructose concentration by sex
nd_TSI_data_2SD_plots %>% ggplot() + geom_point(aes(y= fructose_concentration, x=habitat, color = sex))

nd_TSI_data_2SD_plots %>% ggplot() + geom_point(aes(y= sweeptime, x=habitat, color = time))

#look at differences between time of day, sugar positive and sex - this one relates to the GLMM.#significant difference between sugar positive for (i) afternoon female - afternoon male (ii) morning female - afternoon male (iii) afternoon male - morning male. 

#there was more sugar feeding in the afternoon than the morning. 

#Sweeptime with habitat, filled with sex. Doesn't appear to be significantly different.

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=habitat, y=sweeptime)) + 
  geom_point()

#concentration of fructose by habitat type - no significant difference.
nd_TSI_data_2SD_plots %>% ggplot() + 
  geom_point(aes(x=habitat, y=fructose_concentration, color=sex))


#fructose concentration - by male and female for each habitat type. Maybe difference between Male and Female for urban environment?

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=sex, fill=fructose_concentration)) + geom_bar(position="dodge") 

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=sex, fill=sugar)) + geom_bar(position="dodge") + facet_grid(~fct_rev(time)) + labs(x= "Sex", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()

#final figures examples
```
Plot of flowering sources by station

```{r}
#get the sum of sugar by habitat, station and sex

nd_TSI_data_plots_visual_station_sum <- nd_TSI_data_2SD_plots %>% 
                         group_by(sugar, sex, habitat, station) %>% 
                         summarise(samp = n())

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=station, fill=sugar)) + geom_bar(position="fill") + facet_grid(~habitat+sex) + labs(x= "habitat", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()

#I see no difference between the sugar by each station. Slightly more sugar feeding in residential stations than bush stations. 

#split by sex

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=station, fill=sugar)) + geom_bar(position="fill") + facet_wrap(~sex+habitat) + labs(x= "habitat", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()

#no males were captured in residential station 8. 

#maybe look at fructose concentration by station

nd_TSI_data_2SD_plots %>% ggplot(mapping = aes(x=fructose_concentration, fill=sugar)) + geom_bar(position="fill") + facet_wrap(~sex) + labs(x= "habitat", y = "Count", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive"))+ theme_cowplot()


```

GLMM for the following model 
```{r}
albo_TSI_data_2SD_glmer <- glmer(sugar ~ time*sex+habitat + (1|day) + (1|station), family = binomial, data = albo_TSI_data_2SD)
Anova(albo_TSI_data_2SD_glmer)
summary(albo_TSI_data_2SD_glmer)

hoslem.test(albo_TSI_data_2SD$sugar, fitted(albo_TSI_data_2SD_glmer))

#when using the 2 SD data, the H-L fit is not significant.

```

Plotting the male 2 SD data
```{r}
albo_male_2SD <- read.csv(file = "TSI_data_albo_male_2SD.csv")

albo_male_2SD_plots <- albo_male_2SD %>% mutate(sugar= as.factor(sugar))

#confirm that this is now a factor. 
str(albo_male_2SD_plots)

male_only_2SD <- glmer(sugar ~ time+habitat + (1|day) + (1|station), family = binomial, data = albo_male_2SD)
summary(male_only_2SD)
Anova(male_only_2SD)

#interesting. When I plot this by males only, the significance of habitat is not there. 

hoslem.test(albo_male_2SD$sugar, fitted(male_only_2SD))
#highly insignicant

#time for male albopictus - more male albopictus is sugar fed in the morning. 
albo_male_2SD_plots %>% ggplot(mapping = aes(x=time, fill=sugar)) + geom_bar(position="fill") + scale_x_discrete(limits=positions_time) + labs(x= "Time", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#habitat for male albopictus
albo_male_2SD_plots %>% ggplot(mapping = aes(x=habitat, fill=sugar)) + geom_bar(position="fill") + labs(x= "Habitat", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

```

Plotting the female 2 SD data
```{r}
#Import the data

albo_female_2SD <- read.csv(file = "TSI_data_albo_female_2SD.csv")

#convert this to a factor

#convert the sugar integer to a factor

albo_female_2SD_plots <- albo_female_2SD %>% mutate(sugar= as.factor(sugar))

#confirm that this is now a factor. 
str(albo_female_2SD_plots)

#running the model

female_only_2SD <- glmer(sugar ~ time+habitat + (1|day) + (1|station), family = binomial, data = albo_female_2SD)
summary(female_only_2SD)
Anova(female_only_2SD)

#time and habitat are significant. 

hoslem.test(albo_female_2SD$sugar, fitted(female_only_2SD))
#highly insignicant

#plot sugar feeding by sex and time

#time for females albopictus - more female albopictus is sugar fed in the morning. 
albo_female_2SD_plots %>% ggplot(mapping = aes(x=time, fill=sugar)) + geom_bar(position="fill") + scale_x_discrete(limits=positions_time) + labs(x= "Time", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

#order them by morning and afternoon

positions_time <- c("Morning", "Afternoon")


#habitat for females albopictus - more female albopictus is sugar fed in the urban environment. 
albo_female_2SD_plots %>% ggplot(mapping = aes(x=habitat, fill=sugar)) + geom_bar(position="fill") + labs(x= "Habitat", y = "Proportion", fill= "Sugar fed") + scale_fill_discrete(labels= c("Negative", "Positive")) +theme_cowplot()

```
